%-------------------------
% Full-Stack Engineer Resume - Leonel Guerrero
% Optimized for ATS & Full-Stack + AI Engineering roles (2026)
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.65in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{multicol}

%----------COLORS----------
\definecolor{primary}{HTML}{1a1a2e}
\definecolor{accent}{HTML}{0f3460}
\definecolor{linkcolor}{HTML}{1565C0}

%----------FORMATTING----------
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdfborder={0 0 0}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting
\titleformat{\section}{
    \vspace{-6pt}\scshape\raggedright\large\bfseries\color{primary}
}{}{0em}{}[\color{accent}\titlerule\vspace{-4pt}]

% Subsection formatting
\titleformat{\subsection}[runin]{
    \bfseries
}{}{0em}{}[]

% Custom commands
\newcommand{\resumeHeading}[4]{
    \vspace{-1pt}
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\small #2} \\
        \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{2pt}
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\small #2} \\
        \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItem}[1]{\item\small{#1}\vspace{-2pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%                 DOCUMENT
%-------------------------------------------
\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge\bfseries\color{primary} Leonel Guerrero} \\[6pt]
    {\large Full-Stack Engineer $\cdot$ End-to-End Product Delivery $\cdot$ AI Integration} \\[6pt]
    \small
    \faIcon{map-marker-alt}\ Dallas, TX \quad
    \faIcon{phone}\ +1 (945) 338-0177 \quad
    \faIcon{envelope}\ \href{mailto:leonelisaacguerrero@gmail.com}{leonelisaacguerrero@gmail.com} \\[3pt]
    \faIcon{linkedin}\ \href{https://www.linkedin.com/in/leogcode}{linkedin.com/in/leogcode} \quad
    \faIcon{github}\ \href{https://github.com/leogcode}{github.com/leogcode} \quad
    \faIcon{globe}\ \href{https://leonelguerrero.com}{leonelguerrero.com}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
Full-Stack Engineer with 5+ years shipping production systems end-to-end -- from infrastructure and DevOps through backend APIs to polished frontends. I build and deliver entire products as a one-man army, and I leverage LLMs, agentic workflows, and AI integration to make them 10x more powerful. Proven track record designing scalable APIs, real-time platforms, cross-platform mobile apps, and containerized deployment pipelines. Bilingual (English/Spanish) -- authorized to work in the US (no sponsorship needed).

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
    \textbf{Languages:} & Python, TypeScript, JavaScript, SQL, Java, HTML5, CSS3 \\[3pt]
    \textbf{Frontend:} & React, Next.js, React Native, Tailwind CSS, Zustand, Streaming UI \\[3pt]
    \textbf{Backend:} & Node.js, FastAPI, Django, Spring Framework, REST APIs, GraphQL, WebSockets \\[3pt]
    \textbf{Infrastructure:} & Docker, CI/CD, GitHub Actions, AWS, Vercel, Linux, Nginx, Traefik \\[3pt]
    \textbf{Data \& DBs:} & PostgreSQL, PGVector, MongoDB, Redis, Drizzle ORM, Amazon S3, Pinecone \\[3pt]
    \textbf{AI \& LLM:} & LangChain, LangGraph, RAG Pipelines, Prompt Engineering, Agent Orchestration, Multi-Agent Systems, MCP, Structured Outputs, Function Calling \\[3pt]
    \textbf{Observability:} & OpenTelemetry, Grafana, Grafana Alloy, Loki, Prometheus, Tempo, Alertmanager, Sentry, PostHog \\[3pt]
    \textbf{Tools \& Testing:} & Git, Playwright, Vitest, ESLint, Zod Schema Validation \\
\end{tabularx}

%----------EXPERIENCE----------
\section{Professional Experience}

\resumeSubheading
    {Acid Tango}{April 2025 -- Present}
    {Full Stack Engineer}{Remote}
\resumeItemListStart
    \resumeItem{Ship full-stack applications end-to-end with Next.js, TypeScript, and PostgreSQL -- owning the entire delivery from database schema design through API development to production frontend.}
    \resumeItem{Build real-time streaming interfaces and robust API layers with structured output parsing (Zod schemas), integrating AI capabilities where they create measurable product value.}
    \resumeItem{Implement production monitoring and observability using Sentry and PostHog, ensuring system reliability and data-driven product decisions.}
    \resumeItem{Design and deploy containerized microservice architectures with Docker, managing the full DevOps pipeline for scalable application infrastructure.}
\resumeItemListEnd

\resumeSubheading
    {tiigre App}{January 2024 -- April 2025}
    {Full Stack Engineer \& Mobile Developer}{Caracas, Venezuela}
\resumeItemListStart
    \resumeItem{Shipped cross-platform mobile applications for Android and iOS using React Native, delivering complete products from UI design through API integration to app store deployment.}
    \resumeItem{Built full-stack web applications end-to-end, delivering scalable solutions processing thousands of daily user interactions with sub-second response times.}
    \resumeItem{Collaborated with cross-functional teams to translate business requirements into technical specifications, driving product decisions alongside design and product stakeholders.}
    \resumeItem{Established automated testing pipelines with Playwright and schema-driven validation with Zod, ensuring product reliability across the full stack.}
\resumeItemListEnd

\resumeSubheading
    {Modu, LLC}{January 2022 -- December 2023}
    {Software Engineer}{Caracas, Venezuela}
\resumeItemListStart
    \resumeItem{Developed and shipped production applications across the full stack using React, Node.js, and PostgreSQL, owning features from database design through deployment.}
    \resumeItem{Built and launched a cross-platform mobile application with React Native, expanding the product's reach across iOS and Android from a single codebase.}
    \resumeItem{Led Agile development practices across cross-functional teams, managing iterative delivery cycles and driving sprint-based product releases.}
    \resumeItem{Worked across diverse technology stacks (React, Node.js, PostgreSQL, mobile), building the polyglot engineering foundation for end-to-end product delivery.}
\resumeItemListEnd

\resumeSubheading
    {Self-Employed}{May 2021 -- April 2022}
    {Freelance Software Developer}{Caracas, Venezuela}
\resumeItemListStart
    \resumeItem{Delivered complete web applications for multiple clients across diverse industries as a solo developer -- handling requirements, architecture, development, and deployment end-to-end.}
    \resumeItem{Resolved complex technical challenges including performance optimization and legacy codebase refactoring, consistently exceeding client expectations on scope and timeline.}
    \resumeItem{Adapted rapidly across technology stacks per project requirements, building the versatile engineering foundation for one-person product delivery.}
\resumeItemListEnd

\resumeSubheading
    {HLC Electronic}{September 2018 -- February 2021}
    {Computer Technician}{Caracas, Venezuela}
\resumeItemListStart
    \resumeItem{Troubleshot hardware and software issues across desktop, laptop, and peripheral systems, developing deep systems-level infrastructure understanding.}
    \resumeItem{Installed, configured, and maintained operating systems (Windows, macOS, Linux) and software applications, building the Linux administration skills used in server deployment and DevOps.}
\resumeItemListEnd

%----------EDUCATION----------
\section{Education}

\resumeSubheading
    {Universidad Sim\'{o}n Bol\'{i}var}{September 2018 -- December 2024}
    {Bachelor of Engineering -- Computer Engineering}{Caracas, Venezuela}
\resumeItemListStart
    \resumeItem{Relevant coursework: Algorithms, Data Structures, Distributed Systems, Databases, Software Engineering, Statistics}
\resumeItemListEnd

\resumeSubheading
    {Platzi}{February 2019}
    {Certificate -- Computer Science}{}

%----------PUBLICATIONS----------
\section{Publications}
\resumeSubHeadingListStart
    \item\small\textbf{Energy Optimization through a Multidimensional Distributed Scheduling Approach} -- Research on distributed computing optimization and workload scheduling strategies. \vspace{-2pt}
    \item\small\textbf{An Evaluation of the Impact of End-to-End Query Optimization Strategies on Energy Consumption} -- Research on query optimization with applications to database performance and efficient data retrieval.
\resumeSubHeadingListEnd

%----------CERTIFICATIONS----------
\section{Certifications}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.15in, label={\small\faIcon{certificate}}, itemsep=-2pt]
    \small
    \item Curso de Fundamentos de Bases de Datos
    \item Curso Profesional de Git y GitHub
    \item Curso de Django
    \item Curso de Fundamentos de .NET
    \item Curso de Fundamentos de Electricidad y Electr\'{o}nica
\end{itemize}
\end{multicols}

%----------ADDITIONAL----------
\section{Additional}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
    \small
    \item \textbf{Languages:} English (Fluent), Spanish (Native)
    \item \textbf{Work Authorization:} Authorized to work in the US (valid work permit -- no sponsorship needed)
    \item \textbf{Interests:} End-to-end product delivery, AI-powered product features, open-source tooling, agentic workflows
\end{itemize}

\end{document}
